Interactive Visualization for System Log Analysis

### 2013-12-18 paper/paper.tex
Updated discussion/conclusion

\author{Woojong Koh and Armin Samii\thanks{e-mail:\{wjkoh,samii\}@berkeley.edu}\\University of California, Berkeley}
\pdfauthor{Armin Samii and Woojong Koh}

@@

\section{Implementation}
We identify each log message by the node and source code line that generated it.
We assume that all logs are generated using the Google Logging Library (GLOG)\footnote{\url{https://code.google.com/p/google-glog/}} in order to know which source line generated which log message.
This assumption can be dropped using the mining algorithm of Xu and collaborators~\cite{Xu:2009:OSP:1674659.1677125}.

@@

\section{Discussion}
% What has the audience learned about visualization from your work?

The log data we used in this project came from the system which looks through terabytes of Google
Street View data and uses them for various machine learning tasks. It uses about 80 processes, each
process with its own log file, and spread over around a dozen machines. There are regular failures
which are currently cumbersome to find and debug.

We wanted to create a responsive system which visualizes the state of the system in real-time, is
robust to errors, and can display an arbitrary number of nodes. Not all nodes will be displayable on
a single screen, so the system had to be able to determine areas of interest (e.g. failed nodes,
slow nodes, or completed tasks) in the visualization and direct the user’s attention there. Our
anomaly detection built on Wei Xu's in several ways: (1) their work does not use timestamps, which
we believe are vital to understanding the system’s state; (2) their work intentionally ignores the
ordering of log messages, and instead pays attention only to the number of occurrences of a message
, we hypothesize order may matter; (3) most importantly, their visualizations are more primitive. We
believe the idea of near-infinite zoom (where the most detailed layer essentially shows the
information in the actual log, and as you zoom out, more and more information is aggregated) will
allow a user to explore the system state rapidly.

What we want to point out in this paper is that along with our project there is a direction of
visualization research that can ultimately help system administrators to monitor and analyze the
status of a large distributed system. We think this will become more and more important as the trend
of technology emphasizes on parallelism and distributed system such as cloud computing.

\section{Future Work}
% A description of how your system could be extended.}

We believe automatically determining plot type would be a good improvement for our system because
data extracted from raw log messages can be arbitrary and it is hard to be predetermined by an user.
Also, we want to extend our system to online and real-time analysis and implement more intelligent
features preprocessing. Lastly, it would be great if our system can cluster logs based on more
elaborate features.

\section*{Acknowledgements}
The authors would like to thank Ling Huang for helpful discussions and Sean Arietta for providing us with the log data gathered from his research project.

>>>>

\author{Armin Samii and Woojong Koh\thanks{e-mail:\{samii,wjkoh\}@berkeley.edu}\\University of California, Berkeley}
\pdfauthor{Armin Samii and Woojong Koh}

@@

\section{Implementation}
We identify each log message by the node and source code line that generated it.
We assume that all logs are generated using the Google Logging Library (GLOG)\footnote{\url{https://code.google.com/p/google-glog/}} in order to know which source line generated which log message.
This assumption can be dropped using the mining algorithm of Xu and collaborators~\cite{XuOSP}.

@@

\section{A Note on the Data}

Our goal for this project was to assist in analyzing a specific source of log files, which was a machine learning algorithm on terabytes of data.
The machine learning algorithm used about 80 processes, each with its own log file, and spread over around a dozen machines.
There are regular failures which are currently cumbersome to find and debug.
At the same time, we kept our system general enough to work on other types of log files, particularly one with many more than a dozen nodes.

For this particular application, we believe our system can immensely simplify the analysis of the log data.
Diverging residuals, crashed nodes, and network failures are the common failure cases, and our system can capture all of these.
While other log analysis research often focuses on analysis of a \emph{system} \cite{XuOSP,Xu09}, we also focus on analysis of an \emph{algorithm} which periodically logs its progress.
The failures are then in the variables, not the existence of the message.

\section{Conclusions and Future Work}

We have presented a system for visualizing arbitrary log files.
The log files are automatically and distributedly parsed, features are computed per node, and the results are visualized in an easy-to-use web interface.
We cluster similarly-performing nodes into a single visualization to abstract away redundant data, if the user desires.

The visualization has a spectrum of parameters.
On one end of this spectrum, the raw log data is shown; on the other end, a single graph shows the most representative state of the system.
The importance of this point is \emph{trustworthiness} of the visualization: no data is hidden from the user.

Our visualization is still extremely primitive.
Users may have no intuition as to why two clusters are separated.
Displaying a cluster confidence may assist in telling the user when two clusters are not very different.
On the other hand, if two clusters should be different (such as in the case of a 1\% slowdown of a node), we would want to tell the user more information about why they were clustered differently.
As is, it would be very hard for a user to notice a 1\% slowdown in a node.

We would like to compute more elaborate features for the clustering, including higher-order statistics.
However, as the feature complexity increases, the interactivity decreases.
Finding a middle-ground between interactivity and complexity is an open problem which we are not sure how to address.

Finally, we would need a more thorough evaluation of our visualization.
Some questions we have are:
\begin{enumerate}
    \item is a scatterplot the best visualization choice?
    \item are we able to successfully segregate other types of anomalies in different clusters?
    \item can multiple messages be aggregated into the same plot?
\end{enumerate}

There is a lot to be desired before our system is usable in the wild.
We believe we have taken a major step in the right direction by providing the user with tools to explore the raw log data, rather than trying to predict what they would like to know.

\section*{Acknowledgements}
The authors would like to thank Ling Huang for helpful discussions and insight into the structure of log files,
Sean Arietta for providing us with the log data gathered from his research project,
and John Kubiatowicz and Anthony Joseph for their guidance throughout this project.
Adrien Truielle at Carnegie Mellon University provided the desktop machine on which we ran our experiments.
